### 2018-09-27 paper/introduction.tex
couple of questions

Model-based testing (MBT) is an  active research field that is currently
evaluated and integrated into industrial verification processes by many
companies worldwide. This holds particularly for the embedded and
cyber-physical systems domains, where critical systems require rigorous
testing.

@@

This paper presents complete black-box test suites for software and systems
modelled using CSP. They can be generated for non-terminating, 
divergence-free\footnote{The
assumption of divergence freedom is usually applied in black-box testing,
since it cannot distinguish between divergence and deadlock.}, finite-state
CSP processes with finite alphabets, interpreted both in the trace and the
failures semantics. Our results complement work
in~\cite{DBLP:conf/pts/CavalcantiS17}. There, fault domains are specified as
collections of processes refining a ``most general'' fault domain member.
With that concept, complete test suites may be finite or infinite. This gives
important insight into the theory of fault-domain testing for CSP, but we are
particularly interested in {\it finite} suites when it comes to practical
application. While~\cite{DBLP:conf/pts/CavalcantiS17} may require additional
criteria to select tests from still infinite test suites, here, we further
restrict fault domains using a graph representation of processes (originally
elaborated for model checking) to obtain finite test suites. 
%%%\fixme{alcc: I think termination is not handled either?}

@@

The main contribution of this paper is the construction of two test suites to
verify the conformance relations \emph{trace refinement} and \emph{failures
refinement} for any given non-terminating, 
non-divergent, finite-state, finite alphabet CSP
process. We prove their completeness with respect to fault domains
of the described type.  The existence of -- possibly infinite -- complete
test suites has been established for process algebras, and for CSP in
particular, by several
authors~\cite{Hennessy:1988:ATP:50497,Schneider:1995:OST:203471.203475,DBLP:conf/fm/PeleskaS96,peleska1997a,DBLP:conf/icfem/CavalcantiG07,DBLP:conf/pts/CavalcantiS17}.
To the best of our knowledge, however, this article is the first to present
{\it finite}, complete test suites associated with this class of fault
domains and conformance relations.

Moreover, our result is not a simple transcription of existing knowledge
about finite, complete test suites for finite state machines. The
capabilities of CSP to express nondeterminism in a more fine-grained way than
it is possible for FSMs requires a more complex approach to testing systems
for conformity in the failures-model than it is required for model-based
testing against nondeterministic FSMs, as published, for example,
in~\cite{hierons_testing_2004,DBLP:conf/hase/PetrenkoY14}: CSP distinguishes between 
external choice, where the environment can control the behaviour of a process, and
internal choice where process behaviour is internally decided and cannot be influenced
by the environment. In contrast to this, FSMs specify nondeterministic behaviour
by offering more than one possible output to a given input, and this output can be 
controlled by an FSM representing the environment. Loosely speaking, this corresponds to external choice in CSP, while there is no equivalent to internal choice in nondeterministic FSMs.

Finally, we prove two optimality results.
(1) We show that the
approach to testing the admissibility of an SUT's nondeterministic behaviour
is optimal in the sense that it cannot be established with fewer ``probes'' investigating
the SUT's degree of nondeterminism. These probes are minimal sets of events offered
by the test to the SUT, such that a refusal of the SUT to engage into any of these events
reveals a violation of failures refinement.
(2) Furthermore, it is shown that the maximal length of traces to be investigated in 
a complete test suite cannot be further reduced without loosing the suite's capability to
uncover any violation of trace or faulures  refinement.

%%%\fixme{alcc: I did not understand this?}

@@

\subsubsection*{Overview}
In Section~\ref{section:preliminaries}, we present the background material
relevant to our work. In Section~\ref{sec:finitecompletefails}, finite
complete test suites for verifying failures refinement are presented. Test
suites checking trace refinement are a simplified version of the former
class; they are presented in Section~\ref{sec:finitecomplete}. 
The optimality results are presented in Section~\ref{sec:complexity}, together with further
complexity considerations.
A sample test
suite is presented in Section~\ref{sec:case}. Our results are discussed in
Section~\ref{sec:conc}, where we also conclude. References to related work
are given throughout the paper where appropriate.

>>>>

Model-based testing (MBT) is an active research field; results are currently
being evaluated and integrated into industrial verification processes by many
companies worldwide. This holds particularly for the embedded and
cyber-physical systems domains, where critical systems require rigorous
testing.

@@

This paper presents complete black-box test suites for software and systems
modelled using CSP. They can be generated for non-terminating,
divergence-free, finite-state CSP processes with finite alphabets,
interpreted both in the trace and the failures semantics. Divergence freedom
is usually assumed in black-box testing, since it cannot distinguish between
divergence and deadlock.

Our results complement work in~\cite{DBLP:conf/pts/CavalcantiS17}. There,
fault domains are specified as collections of processes refining a ``most
general'' fault domain member. With that concept, complete test suites may be
finite or infinite. This result gives important insight into the theory of
fault-domain testing for CSP, but we are particularly interested in {\it
finite} suites when it comes to practical application.
While~\cite{DBLP:conf/pts/CavalcantiS17} may require additional criteria to
select tests from still infinite test suites, here, we further restrict fault
domains using a graph representation of processes (originally elaborated for
model checking) to obtain finite test suites.

@@

The main contribution of this paper is the construction of two test suites to
verify the conformance relations \emph{trace refinement} and \emph{failures
refinement} for any given non-terminating, non-divergent, finite-state,
finite alphabet CSP process. We prove their completeness with respect to
fault domains of the described type.  The existence of -- possibly infinite
-- complete test suites has been established for process algebras, and for
CSP in particular, by several
authors~\cite{Hennessy:1988:ATP:50497,Schneider:1995:OST:203471.203475,DBLP:conf/fm/PeleskaS96,peleska1997a,DBLP:conf/icfem/CavalcantiG07,DBLP:conf/pts/CavalcantiS17}.
To the best of our knowledge, this article is the first to present {\it
finite}, complete test suites associated with this class of fault domains and
conformance relations.

Our result is not a simple transcription of existing knowledge about finite,
complete test suites for FSMs. The capabilities of CSP to express
nondeterminism in a more fine-grained way than it is possible for FSMs
requires a more complex approach to testing for conformity in the
failures-model than required for model-based testing against nondeterministic
FSMs, as published, for example,
in~\cite{hierons_testing_2004,DBLP:conf/hase/PetrenkoY14}. CSP distinguishes
between external choice, where the environment can control the behaviour of a
process, and internal choice where the behaviour is decided internally and
cannot be influenced by the environment. In contrast, FSMs specify
nondeterministic behaviour by offering more than one possible output for a
given input, and this output can be controlled by an FSM representing the
environment. Loosely speaking, this corresponds to external choice in CSP,
while there is no equivalent to internal choice in nondeterministic FSMs.
\fixme{alcc: I'm slightly uncomfortable with this claim. Can the environment
really control outputs? Do you not have tau (internal) events in FSM? I'm
unsure, but you guys know about FSMs much more than I do.}

Finally, we prove two optimality results here. (1)~We show that our approach
to testing the admissibility of an SUT's nondeterministic behaviour is
optimal in the sense that it cannot be established with fewer ``probes''
investigating the SUT's degree of nondeterminism. These probes are minimal
sets of events offered by the tests to the SUT, such that a refusal of the
SUT to engage into at least one of these events reveals a violation of
failures refinement. (2)~Furthermore, it is shown that the maximal length of
traces to be investigated in a complete test suite cannot be further reduced
without loosing the suite's capability to uncover any violation of trace or
failures refinement.

@@

\subsubsection*{Overview}
In Section~\ref{section:preliminaries}, we present the background 
relevant to our work. In Section~\ref{sec:finitecompletefails}, finite
complete test suites for verifying failures refinement are presented. Test
suites checking trace refinement are a simplified version of the former
class; they are presented in Section~\ref{sec:finitecomplete}.
The optimality results are presented in Section~\ref{sec:complexity}, together with further
complexity considerations.
A sample test
suite is presented in Section~\ref{sec:case}. Our results are discussed in
Section~\ref{sec:conc}, where we also conclude. References to related work
are given throughout the paper where appropriate.
